\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{Security Analyst Internship \hfill NOV 2023 --- MAY 2024}
\subtext{Winona IT \hfill Warsaw, IN}
\begin{zitemize}
\item Assisted in the roll-out of CrowdStrike Falcon across customer's environment
\item Installed Falcon Sensors on Windows and Linux Systems
\item Monitored and responded to alerts in Microsoft Entra, Malwarebytes, and Falcon
\item Drafted project proposal and completed deployment of a CrowdStrike SIEM Connector
\item Manually collected Falcon data via FalconPy into JSON format 
\item Conducted email analysis and tracing, data research, and reporting.
\item Worked with technical lead to perform threat hunts.
\item Responded and worked with security operations regarding security incidents.
\end{zitemize}

%====================
% EXPERIENCE B
%====================

\subsection{Digital Forensics Internship \hfill SEP 2022 --- NOV 2023}
\subtext{Allen County Prosecuting Attorney's High Tech Crime Unit \hfill Fort Wayne, IN}
\begin{zitemize} 
\item Forensically preserved laptops, desktops, mobile devices, and DVRs.
\item Analyzed and compiled complex data into formats for investigative tasks, including mobile application data such as timestamps, database entries, deleted messages, notifications, screen orientations, elevation changes, health metrics, and encrypted messaging from Signal and WhatsApp.
\item Delivered detailed reports and portable cases to detectives, deputy prosecutors, and defense attorneys for use in criminal investigations and court hearings.
\item Established good working relationships with detectives and deputy prosecutors to expand the reach of the High Tech Crime Units services.
\item Utilized digital intelligence tools such as GrayKey, Cellebrite, Magnet Forensics, Belkasoft, Oxygen Forensics and Autopsy. 
\item Applied creative thinking with knowledge of mobile applications, encryption, python scripting and SQL databases to solve problems not addressed by the forensic software.
\item Assisted in establishing a workflow for the High Tech Crime Unit and discussed ideas for how the unit can better serve the surrounding counties. 
\item Presented testimony for the Honorable Steven O. Godfrey as an expert witness in State of Indiana v. Demontra Moore (Case: 02D04-2304-F2-000023)
\end{zitemize}

\newpage
\vspace*{-\baselineskip}
\thispagestyle{empty}
\vspace{-60px}

%====================
% EXPERIENCE C
%====================
\subsection{Cybersecurity Architect Internship \hfill JAN 2022 --- SEP 2022}
\subtext{Pixpher LLC \hfill Fort Wayne, IN}
\begin{zitemize}
\item Created a vulnerability disclosure policy
\item Created a database migration plan
\item Developed Standard Operating Procedures in regards to Information Security
\item Drafted AppSec best practices document
\end{zitemize}


%====================
% EXPERIENCE D
%====================

\subsection{DevOps Assistant Workstudy \hfill AUG 2021 --- JAN 2022}
\subtext{Indiana Institute of Technology \hfill Fort Wayne, IN}
\begin{zitemize}
\item Migrated MySQL database
\item Setup a self-service password reset service in Windows Datacenter 2022
\item Developed thelinuxarchive.com
\end{zitemize}

\end{document}

